---
title: "STA305A1"
author: "Qizheng Wang"
date: "2/4/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## STA305 Assignment 1, student
### Student number 1002079877

## Question A
``` {r question A}
set.seed(9877)
Number<-c(1:8)
S<-round(rnorm(8,mean=5,sd=2),3)
T<-round(rnorm(8,mean=7,sd=2),3)
diff<-S-T
compD<-data.frame(Number,S,T,diff)

plot(compD$Number,compD$S,col="red",cex=1.2,xlab="Number of Treatment",ylab="Values")
points(compD$Number,compD$T,col="blue",cex=1.2)
legend("bottomleft",legend=c("S","T"),text.col=c("red","blue"),cex = 0.7)

compD
```

### (1)-(4)
The seed is 9877.\newline
The first treatment S is `r S`.\newline
The second treatment T is `r T`.\newline
The oberservation is compD.


## Question B

### Question B(i)
```{r Question B(i)}
## Randomized pair design
meandiff<-mean(diff)
ST<-c(S,T)
N <- 2^8
res <- numeric(N)
LR=list(c(-1,1))
trtassign<-expand.grid(rep(LR,8))
for(i in 1:N)
{
  res[i]<-mean(as.numeric(trtassign[i,])*diff)
}
summary(res)

##Completely randomized design
comp<-c(S,T)
N <- choose(16,8)
res2 <- numeric(N)
observed=mean(S)-mean(T)
index <-combn(1:16,8)
for (i in 1:N){
  res2[i] <- mean(comp[index[,i]])-mean(comp[-index[,i]])
}

```
The first design is the randomized pair design.\newline
There are $2^8$=`r 2^8` values in this distribution, and the probability of the observed treatment allocation is $\frac{1}{2^8}$=`r 1/(2^8)`.\newline
The second design is the Completely randomized design.\newline
There are 	$\binom{16}{8}$=`r choose(16,8)` values in this distribution, and the probability of the observed treatment allocation is $\frac{1}{\binom{16}{8}}$=`r 1/choose(16,8)`.\newline

### Question B(ii)
``` {r Question B(ii)}
## Randomized paired design
hist(res,xlab='Difference in mean',ylab="Number",main="Randomization Distribution for Paired Comparison")
abline(v = meandiff, col = 'red')
abline(v = -meandiff, col = 'red')
tbar<-mean(res)
p_val<-sum(abs(res-tbar)>=abs(meandiff-tbar))/N
round(p_val,4)

## Completely randomized design
hist(res2,xlab = 'Difference in main', main = 'Randomization Distribution for Completely Randomized Design')
abline(v=observed, col='blue') 
abline(v=-observed, col='blue') 
tbar2<-mean(res2)
p_val2<-sum(abs(res2-tbar2)>=abs(observed-tbar2))/N
round(p_val2,4)
```
By doing a two-sided randomization test, the p-value for the randomized paired design is `r p_val2`. The significance level I choose will be 0.05 based on the rule of thumb. Thus `r p_val2` is smaller than 0.05, thus reject the null hypothesis, meaning there are difference in means for two treatments.

## Question C
``` {r Question C}
#paired t test
t.test(S,T, paired=TRUE)
#two sample t test
t.test(S,T)
```

### Question C(i)
For the completely randomdized design, because the population distribution is normal, thus an appropriate test will be two sample t-test.\newline
$H_0$: the mean of two sample is equal to zero.\newline
$H_a$: true difference in means is not equal to 0.\newline
P-value at here is `r t.test(S,T)$p.value`. The p-value heare means under the assumption that the population means are equal,the probability that hte difference between the sample means is at least as large as what has been observed.
\newline
\newline
For the paried design, paired t test should be conducted.\newline
$H_0$: the mean of two sample is equal to zero.\newline
$H_a$: true difference in means is not equal to 0.\newline
P-value at here is `r t.test(S,T, paired=TRUE)$p.value`.\newline

### Question C(ii)
Because the distribution is normal and two samples are independent, the normality and independenty are satisfied for the two-sample t test.
But since the parameters are unknown, the variance may not be the same.

### Quesetion C(iii)
The two-sided randomization test has a p-value of `r p_val2`, while the p-value of t-test is `r t.test(S,T)$p.value`, it's almost identical, and they are all smaller than $\alpha=0.05$, thus the results are consistent.
