---
title: "STA305A1"
author: "Qizheng Wang"
date: "2/4/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## STA305 Assignment 1, student
### Studetn number 1002079877

## Question A
``` {r question A}
set.seed(9877)
Number<-c(1:8)
TreatS<-round(rnorm(8,mean=5,sd=2),3)
TreatT<-round(rnorm(8,mean=7,sd=2),3)
diff<-TreatS-TreatT
compD<-data.frame(Number,TreatS,TreatT,diff)

plot(compD$Number,compD$TreatS,col="red",cex=1.2,xlab="Number of Treatment",ylab="Values")
points(compD$Number,compD$TreatT,col="blue",cex=1.2)
legend("bottomleft",legend=c("S","T"),text.col=c("red","blue"),cex = 0.7)

compD
```
### (1)-(4)
The seed is 9877.\newline
The first treatment S is `r TreatS`.\newline
The second treatment T is `r TreatT`.\newline
The oberservation is compD.

## Question B
```{r Question }
## Paried distribution
ST<-c(TreatS,TreatT)
N <- 2^8
res <- numeric(N)
LR=list(c(-1,1))
trtassign<-expand.grid(rep(LR,8))
for(i in 1:N)
{
  res[i]<-mean(as.numeric(trtassign[i,])*compD$diff)
}

## Two sample randomization
N2 <- choose(16,8)
res2 <- numeric(N2)
observed=mean(TreatS)-mean(TreatT)
index <-combn(1:16,8)
for (i in 1:N)
{res[i] <- mean(res2[index[,i]])-mean(res2[-index[,i]])}

```

### Quetion B(i)
The number of value this distribution contain is $\binom{16}{8}$=`r choose(16,8)`.\newline
res contains all the value in this randomization distribution.\newline
The probability of the observed treatment allocation is 

### Question B(ii)
```{r Question 2ii}
## Paired graph
hist(res,xlab='Difference in mean',ylab="Number",main="Randomization Distribution for Paired Comparison")
meandiff=mean(compD$diff)
abline(v = meandiff, col = 'red')
abline(v = -meandiff, col = 'red')
tbar<-mean(res)
p_val<-sum(abs(res-tbar)>=abs(meandiff-tbar))/N
round(p_val,4)

## Two sample graph
hist(res,xlab = "Difference in main", main = "Randomization Distribution")
abline(v=observed, col='blue') 
abline(v=-observed, col='blue') 
tbar2<-mean(res2)
p_val2<-sum(abs(res2-tbar2)>=abs(observed-tbar2))/N
round(p_val,4)
```

### Question C
``` {r Question 2ii}
#paired t test
t.test(TreatS,TreatT, paired=TRUE)
#two sample t test
t.test(TreatS,TreatT)
```